Parameters estimation via HOSVD

### 2024-12-04 Code/R/Research/HOSVD parameters estimate.Rmd
Added ho-esprit plots
Saved data for rrmse results

---
title: "Parameters estimation via HOSVD"
output: html_document
---
```{r, setup, include=FALSE}
library(Rssa)
library(rTensor)
library(ggplot2)
library(gridExtra)
library(factoextra)
library(dplyr)
library(tidyr)
library(waldo)

@@

@@

## Графики RRMSE
```{r}
rate1.df <- rate1.rrmse |> as.data.frame() |> 
   mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "estim dim", names_prefix = "V", values_to = "RRMSE")

>>>>

---
title: "Parameters estimation via HOSVD"
output: html_document
---
```{r, setup, include=FALSE}
library(Rssa)
library(rTensor)
library(ggplot2)
library(gridExtra)
library(factoextra)
library(dplyr)
library(tidyr)
library(waldo)
library(beepr)

@@

close(pb)
beep()
save(
  rate1.rrmse,
  rate2.rrmse,
  freq1.rrmse,
  freq2.rrmse,
  file = paste0("./Research/comp_results/dim_rrmse", plot.name, "_tens.RData")
)
```

@@

close(pb)
save(
  rate1.ssa.rrmse,
  rate2.ssa.rrmse,
  freq1.ssa.rrmse,
  freq2.ssa.rrmse,
  file = paste0("./Research/comp_results/dim_rrmse", plot.name, "_ssa.RData")
)
```

## Графики RRMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 1

load(file = paste0("./Research/comp_results/dim_rrmse", pltnms[pn], "_tens.RData"))
load(file = paste0("./Research/comp_results/dim_rrmse", pltnms[pn], "_ssa.RData"))
```

```{r}
rate1.df <- rate1.rrmse |> as.data.frame() |> 
   mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "estim dim", names_prefix = "V", values_to = "RRMSE")
